paper-graphs

### 2020-02-12 Report/paper-graphs.Rmd
Updates graphs for the paper

#green, violet, blue, yellow, pink, dark blue
estimote_pal <- c('#b6d6c1', '#54003d','#93d5f6','#d5d215','#f3aacb','#2d2556')
theme_set(theme_minimal() + theme(axis.text=element_text(size=14),
        axis.title=element_text(size=16)))

@@

## 5a
```{r}
ggplot(only_blocks(sub_walk_all_factor, 1:3), aes(x = graph.exp_block_id, y = errors, fill = graph.exp_block_id)) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(0.95), geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_dodge(width=0.95),geom="bar") +
  ylab("Average visitation errors") + xlab("Learning condition") + 
  scale_fill_manual(values=estimote_pal,"Block") + guides(fill=F) +
  facet_wrap(~graph.learning.condition, strip.position = "bottom", scales = "free_x") + 
  theme(panel.spacing = unit(0, "lines"), 
         strip.background = element_blank(),
         strip.placement = "outside")
```

## 5b
```{r}
# Pre transfer plot of normalised distances
ggplot(only_blocks(sub_walk_all_factor, 1:3), aes(x = graph.exp_block_id, y = min_norm_distance, fill = graph.exp_block_id)) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(0.95), geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_dodge(width=0.95),geom="bar") +
  ylab("Average normalised trial distance") + xlab("Learning condition") + 
  scale_fill_manual(values=estimote_pal,"Block") + guides(fill=F) +
  facet_wrap(~graph.learning.condition, strip.position = "bottom", scales = "free_x") + 
  theme(panel.spacing = unit(0, "lines"), 
         strip.background = element_blank(),
         strip.placement = "outside")

```

@@

```{r}
ggplot(point_data_1, aes(x = graph.learning.condition, y = abs_error, fill = graph.learning.condition)) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(0.95), geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_dodge(width=0.95),geom="bar") +
  ylab("Average pointing error after learning phase") + xlab("Learning condition") + 
  scale_fill_manual(values = estimote_pal, "Learning condition") +
  guides(fill=F) + theme(axis.title.y = element_text(size = rel(0.9)))

```

## 6a
```{r}
ggplot(only_blocks(sub_walk_all_factor, 3:4), aes(x = graph.exp_block_id, y = errors, fill = graph.exp_block_id)) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(0.95), geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_dodge(width=0.95),geom="bar") +
  ylab("Average visitation errors") + xlab("Learning condition") + 
  scale_fill_manual(values=estimote_pal,"Block") + guides(fill=F) +
  facet_wrap(~graph.learning.condition, strip.position = "bottom", scales = "free_x") + 
  theme(panel.spacing = unit(0, "lines"), 
         strip.background = element_blank(),
         strip.placement = "outside")
```

## 6b
```{r}
### graphs
ggplot(only_blocks(sub_walk_all_factor, 3:4), aes(x = graph.exp_block_id, y = min_norm_distance, fill = graph.exp_block_id)) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(0.95), geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_dodge(width=0.95),geom="bar") +
  ylab("Average normalised trial distance") + xlab("Learning condition") + 
  scale_fill_manual(values=estimote_pal,"Block") + guides(fill=F) +
  facet_wrap(~graph.learning.condition, strip.position = "bottom", scales = "free_x") + 
  theme(panel.spacing = unit(0, "lines"), 
         strip.background = element_blank(),
         strip.placement = "outside")

```

@@

```{r, fig.width=10, fig.height=8}
ggplot(only_blocks(walk_all, 6), aes(x = testing.condition, y = min_norm_distance, fill = graph.learning.condition)) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(0.95), geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_dodge(width=0.95),geom="bar") +
  ylab("Average path distance in the last block of the transfer phase") + xlab("Transfer condition") + 
  scale_fill_manual(values = estimote_pal, "Condition")  + guides(fill=F) + 
  facet_wrap(~graph.learning.condition, strip.position = "top", scales = "free_x") + 
  ggtitle("Learning condition")+
  theme(panel.spacing = unit(0, "lines"), 
         strip.background = element_blank(),
         strip.placement = "outside",
         strip.text = element_text(size = 16),
          plot.title = element_text(hjust = 0.5))

```

##• 7b

```{r}
ggplot(only_blocks(walk_all, 6), aes(x = testing.condition, y = errors, fill = graph.learning.condition)) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(0.95), geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_dodge(width=0.95),geom="bar") +
  ylab("Average number of visitation errors in the last block of the transfer phase") + xlab("Transfer condition") + 
  scale_fill_manual(values = estimote_pal, "Condition")  + guides(fill=F) + 
  facet_wrap(~graph.learning.condition, strip.position = "top", scales = "free_x") + 
  ggtitle("Learning condition")+
  theme(panel.spacing = unit(0, "lines"), 
         strip.background = element_blank(),
         strip.placement = "outside",
         strip.text = element_text(size = 16),
          plot.title = element_text(hjust = 0.5))
```

>>>>

#green, violet, blue, yellow, pink, dark blue
estimote_pal <- c('#b6d6c1', '#54003d','#93d5f6','#d5d215','#f3aacb','#2d2556')
theme_set(theme_minimal() + 
          theme(axis.text=element_text(size=14),
                axis.title=element_text(size=16),
                axis.title.y = element_text(size=20),
                strip.text.x = element_text(size=20),
                plot.subtitle = element_text(hjust = 1, vjust = 0, size = 18, face = "italic"))
          )

@@

## 5a
```{r, fig.width=10, fig.height=8}
ggplot(only_blocks(sub_walk_all_factor, 1:3), aes(x = graph.exp_block_id, y = errors, fill = graph.exp_block_id)) +
  stat_summary(fun.y=mean,position=position_dodge(width=0.95), geom="bar") +
  stat_summary(fun.data=mean_se, position=position_dodge(0.95), geom="errorbar", width = 0.2, size = 1.25) + 
  facet_wrap(~graph.learning.condition, strip.position = "bottom", scales = "free_x") + 
  scale_fill_manual(values=estimote_pal,"Block") + guides(fill=F) +
  labs(x = NULL, y ="Average number of visitation errors", subtitle = "5a") +
  theme(panel.spacing = unit(0, "lines"), 
         strip.background = element_blank(),
         strip.placement = "outside")
```

## 5b
```{r, fig.width=10, fig.height=8}
# Pre transfer plot of normalised distances
ggplot(only_blocks(sub_walk_all_factor, 1:3), aes(x = graph.exp_block_id, y = min_norm_distance, fill = graph.exp_block_id)) +
  stat_summary(fun.y=mean,position=position_dodge(width=0.95), geom="bar") +
  stat_summary(fun.data=mean_se, position=position_dodge(0.95), geom="errorbar", width = 0.2, size = 1.25) + 
  facet_wrap(~graph.learning.condition, strip.position = "bottom", scales = "free_x") + 
  scale_fill_manual(values=estimote_pal,"Block") + 
  labs(x = NULL, y = "Average normalised trial distance", subtitle = "5b") +
  guides(fill=F) +
  theme(panel.spacing = unit(0, "lines"), 
         strip.background = element_blank(),
         strip.placement = "outside")
```

@@

```{r, fig.width=10, fig.height=8}
ggplot(point_data_1, aes(x = graph.learning.condition, y = abs_error, fill = graph.learning.condition)) +
  stat_summary(fun.y=mean, position=position_dodge(width=0.95), geom="bar") +
  stat_summary(fun.data=mean_se, position=position_dodge(0.95), geom="errorbar", width = 0.2, size = 1.25) + 
  scale_fill_manual(values = estimote_pal, "Learning condition") +
  labs(x = NULL, y = "Average pointing error after learning phase", subtitle = "5c") +
  guides(fill=F) + 
  theme(axis.text.x = element_text(size=18, color= "black"))
```

## 6a

```{r, fig.width=10, fig.height=8}
ggplot(only_blocks(sub_walk_all_factor, 3:4), aes(x = graph.exp_block_id, y = errors, fill = graph.exp_block_id)) +
  stat_summary(fun.y = mean,position=position_dodge(width = 0.95),geom="bar") +
  stat_summary(fun.data = mean_se, position = position_dodge(0.95), geom="errorbar", width = 0.2, size = 1.25) + 
  scale_fill_manual(values = estimote_pal,"Block") + 
  facet_wrap(~graph.learning.condition, strip.position = "bottom", scales = "free_x") + 
  labs(x=NULL, y = "Average number of visitation errors", subtitle = "6a") +
  guides(fill = F) +
  theme(panel.spacing = unit(0, "lines"), 
        strip.background = element_blank(),
        strip.placement = "outside")
```

## 6b
```{r, fig.width=10, fig.height=8}
### graphs
ggplot(only_blocks(sub_walk_all_factor, 3:4), aes(x = graph.exp_block_id, y = min_norm_distance, fill = graph.exp_block_id)) +
  stat_summary(fun.y=mean,position=position_dodge(width=0.95),geom="bar") +
  stat_summary(fun.data=mean_se, position=position_dodge(0.95), geom="errorbar", width = 0.2, size = 1.25) + 
  scale_fill_manual(values=estimote_pal,"Block") + 
  facet_wrap(~graph.learning.condition, strip.position = "bottom", scales = "free_x") + 
  labs(x= NULL, y = "Average normalised trial distance", subtitle = "6b") +
  guides(fill = F) +
  theme(panel.spacing = unit(0, "lines"), 
         strip.background = element_blank(),
         strip.placement = "outside")
```

@@

```{r, fig.width=10, fig.height=8}
only_blocks(walk_all, 6) %>%
  select(testing.condition, min_norm_distance, graph.learning.condition) %>%
  rbind(data.frame(testing.condition = "Immersive VR", graph.learning.condition="Desktop", min_norm_distance = NA)) %>%
  ggplot(aes(x = testing.condition, y = min_norm_distance, fill = testing.condition)) +
  stat_summary(fun.y=mean,position=position_dodge(width=0.95),geom="bar") +
  stat_summary(fun.data=mean_se, position=position_dodge(0.95), geom="errorbar", width = 0.2, size = 1.25) + 
  scale_fill_manual(values = estimote_pal, "Transfer condition") +
  facet_wrap(~graph.learning.condition, strip.position = "bottom", scales = "free_x") +
  labs(x = NULL, y = "Average path distance in the last\n block of the transfer phase", subtitle = "7a") + 
  theme(panel.spacing = unit(0, "lines"),
        strip.background = element_blank(),
        strip.placement = "outside",
        legend.position = "top",
        legend.title = element_text(size = 16),
        legend.text = element_text(size = 16),
        axis.text.x = element_blank(),
        strip.text = element_text(size = 16),
        plot.title = element_text(hjust = 0.5))
```

## 7b

```{r, fig.width=10, fig.height=8}
only_blocks(walk_all, 6) %>%
  select(testing.condition, errors, graph.learning.condition) %>%
  rbind(data.frame(testing.condition = "Immersive VR", graph.learning.condition="Desktop", errors = NA)) %>% 
  ggplot(aes(x = testing.condition, y = errors, fill = testing.condition)) +
  stat_summary(fun.y = mean, position = position_dodge(width=0.95), geom = "bar") +
  stat_summary(fun.data = mean_se, position=position_dodge(0.95), geom="errorbar", width = 0.2, size = 1.25) +
  facet_wrap(~graph.learning.condition, strip.position = "bottom", scales = "free_x") +
  scale_fill_manual(values = estimote_pal, "Transfer condition") +
  labs(x = NULL, y = "Average number of visitation errors in\n the last block of the transfer phase", subtitle = "7b") +
  theme(panel.spacing = unit(0, "lines"),
        strip.background = element_blank(),
        strip.placement = "outside",
        legend.position = "top",
        legend.title = element_text(size = 16),
        legend.text = element_text(size = 16),
        axis.text.x = element_blank(),
        strip.text = element_text(size = 16),
        plot.title = element_text(hjust = 0.5))
```
